---
title: "IMDb Ratings and Netflix"
format: html
editor: visual
---

## The Data

The `imdb_top_1000` dataset contains information on the top 1000 movies and TV shows ranked by IMDb rating. The dataset includes details such as movie titles, release years, genres, runtime, IMDb ratings, directors, cast members, number of votes, gross earning, and short plot summaries. The data provides insights into some of the highest rated and most popular films according to IMDb users. 

The `netflix_titles` dataset contains information on movies and TV shows available on Netflix. The dataset includes details about titles, directors, cast members, release years, ratings, duration, genres, and descriptions. It provides an overview of the content available on one of the world's largest streaming platforms. 

## Load Data and Packages  
```{r}

```

## Question 1- Cleaning the Data
Use one dplyr pipeline to clean each dataset 

For IMDb dataset:
- remove rows with missing IMDb ratings
- remove `min` from `Runtime` values and convert it to numeric variable called `runtime_min`
- save cleaned dataset as `imdb_clean`

For Netflix dataset:
- remove rows with missing titles or release years
- convert `date_added` into a date variable 
- rename `listed_in` to `genres`
- save cleaned dataset as `netflix_clean`

```{r}

```

## Question 2

```{r}

```

## Question 3

```{r}

```

